### 2016-05-20 paper/paper.tex
Discuss why the PAY_TO_DDoSer will pick a good difficulty

@@

A target's initial difficulty in DDoSCoin is decided by the stakeholder that
introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
set the difficulty too low, as the DDoS would be innefective. Also, many coins would be
mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
there will be a delay as other domains are mined, and the difficulty adjusts down
to the appropriate level.

>>>>

The bounty poster must select a difficulty that is appropriate for the target
and reward. If the difficulty is too high, no miner will attack the target,
because the miners do not want to waste effort. Also, if the difficulty is
too low, the reward will be claimed for little degradation of service.

@@

A target's initial difficulty in DDoSCoin is decided by the stakeholder that
introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
set the difficulty too low, as the DDoS would be innefective. Also, many coins would be
mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
there will be a delay as other domains are mined, and the difficulty adjusts down
to the appropriate level. These are similar to the incentives for PAY\_TO\_DDOS 
transactions, mentioned in Section~\ref{sec:pay-to-ddos}.
